Supporting Information : Asymmetric tail association in extreme climatic events affects population-extinction risk

### 2019-10-24 SuppMat.Rmd
response added

@@

# flip Clayton copula 
mtc_r<-1-mtc_l
```

@@

# for plotting purpose I just showed only first 500 points
pdf("./Results/introfig_copula.pdf", height=3, width=12)
op<-par(mfrow=c(1,4),mar=c(6,6,2,2),mgp=c(3,1,0))

# extreme left tail
plot(xtc_l[1:500,1],xtc_l[1:500,2],col=rgb(0,0,0,0.1),pch=19,xlab="u",ylab="v",cex.lab=2.5,cex.axis=2)
legend(x="topleft",legend="A",bty="n",cex=2.5)

# moderate left tail
plot(mtc_l[1:500,1],mtc_l[1:500,2],col=rgb(0,0,0,0.1),pch=19,xlab="u",ylab="v",cex.lab=2.5,cex.axis=2)
legend(x="topleft",legend="B",bty="n",cex=2.5)

# moderate right tail
plot(mtc_r[1:500,1],mtc_r[1:500,2],col=rgb(0,0,0,0.1),pch=19,xlab="u",ylab="v",cex.lab=2.5,cex.axis=2)
legend(x="topleft",legend="C",bty="n",cex=2.5)

# extreme right tail
plot(xtc_r[1:500,1],xtc_r[1:500,2],col=rgb(0,0,0,0.1),pch=19,xlab="u",ylab="v",cex.lab=2.5,cex.axis=2)
legend(x="topleft",legend="D",bty="n",cex=2.5)

saveRDS(ktau_common,"./Results/ktau_common.RDS")
```

>>>>

saveRDS(ktau_common,"./Results/ktau_common.RDS")

@@

# flip Clayton copula 
mtc_r<-1-mtc_l

# calculate tau with sampling variation
kcor_el<-cor(xtc_l,xtc_l,method = "kendall")
kcor_el<-kcor_el[1,2]

kcor_er<-cor(xtc_r,xtc_r,method = "kendall")
kcor_er<-kcor_er[1,2]

kcor_ml<-cor(mtc_l,mtc_l,method = "kendall")
kcor_ml<-kcor_ml[1,2]

kcor_mr<-cor(mtc_r,mtc_r,method = "kendall")
kcor_mr<-kcor_mr[1,2]
```

@@

# for plotting purpose I just showed only first 500 points

pdf("./Results/introfig_copula.pdf", height=3, width=12)
op<-par(mfrow=c(1,4),mar=c(6,6,2,2),mgp=c(3,1,0))

# extreme left tail
plot(xtc_l[1:500,1],xtc_l[1:500,2],col=rgb(0,0,0,0.1),pch=19,xlab="u",ylab="v",cex.lab=2.5,cex.axis=2)
#legend(x="topleft",legend="A",bty="n",cex=2.5)
text(x=0.1,y=0.9,"A",cex=2.5)
text(x=0.8,y=0.1,round(kcor_el,4),cex=2)

# moderate left tail
plot(mtc_l[1:500,1],mtc_l[1:500,2],col=rgb(0,0,0,0.1),pch=19,xlab="u",ylab="v",cex.lab=2.5,cex.axis=2)
text(x=0.1,y=0.9,"B",cex=2.5)
text(x=0.8,y=0.1,round(kcor_ml,4),cex=2)

# moderate right tail
plot(mtc_r[1:500,1],mtc_r[1:500,2],col=rgb(0,0,0,0.1),pch=19,xlab="u",ylab="v",cex.lab=2.5,cex.axis=2)
text(x=0.1,y=0.9,"C",cex=2.5)
text(x=0.8,y=0.1,round(kcor_mr,4),cex=2)

# extreme right tail
plot(xtc_r[1:500,1],xtc_r[1:500,2],col=rgb(0,0,0,0.1),pch=19,xlab="u",ylab="v",cex.lab=2.5,cex.axis=2)
text(x=0.1,y=0.9,"D",cex=2.5)
text(x=0.8,y=0.1,round(kcor_er,4),cex=2)
